%based on imperial example provided + hra example at http://www.hra-decisiontools.org.uk/consent/        examples.html 
 \documentclass[a4paper,10pt]{article}
 
 %set font to Arial
 %\usepackage{fontspec}
 %\setmainfont{Arial}
 \usepackage{helvet}
 \renewcommand{\familydefault}{\sfdefault}
 
 %graphics
 \usepackage{graphicx}
 %\usepackage{subfigure}
 \usepackage{pslatex}
 \usepackage{pstricks}
 
 %math equations
 \usepackage{amsmath}
 
 %python code
 %\usepackage{minted}
 
 %headers
 \usepackage{fancyhdr}
 \pagestyle{fancy}
 \lhead{IRAS Project ID: 203355}
 \chead{}
 \rhead{clinicaltrials.gov reference}
 \lfoot{PPS}
 \cfoot{Participant Consent Form v0.1}
 \rfoot{7th August, 2017}
 
 
 %display URLS
 \usepackage{url}
 
 %hyperlinks
 \usepackage{hyperref}
 
 %comments
 \usepackage{verbatim}
 
 %nice tables
 \usepackage{booktabs}
 \newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
 
 %multi rows for the nice tables
 %\usepackage{multirow} 
 
 %nice diplay of code
 %\usepackage{minted}

%nice references
 \usepackage[super]{natbib}
 
 %some maths
 \usepackage{amsmath}
 
 %margins
 %\usepackage{geometry}
 %\geometry{verbose,a4paper,tmargin=60mm,bmargin=25mm,lmargin=25mm,rmargin=25mm}
 
 %in line citations
 %\usepackage{bibentry}
 
 %\hyphenpenalty=10000
 
 %\nobibliography*


 \begin{document}

 \newpage\title{\bf INFORMED CONSENT FORM FOR SUBJECTS ABLE TO GIVE CONSENT}
 \date{}
 %\author{Carl Reynolds \\
 %\small National Heart \& Lung Institute, Imperial College London }
 
 %\pagenumbering{gobble}
 
 \pagestyle{fancy}
 
 %\pagestyle{empty}
 
% \maketitle
 \begin{centering} 
 \section*{INFORMED CONSENT FORM \\ FOR SUBJECTS ABLE TO GIVE CONSENT}
 \end{centering}

 \subsection*{Idiopathic Pulmonary Fibrosis Job Exposure Study (PPS)}

 \vspace{0.2cm}

 \subsubsection*{Name of Principle Investigator: \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}

 \vspace{0.1cm}

 \hfill \textbf{Please initial box}

 \begin{enumerate}
  \item I confirm that I have read and understand the subject information sheet dated
	\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ version \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ for the  above study and have had the opportunity to ask questions which have been answered fully.\hfill \framebox(20,12){}
  \item I understand that my participation is voluntary and I am free to withdraw at any time,	
	without giving any reason, without my medical care or legal rights being affected.\hfill \framebox(20,12){}
  \item I understand that sections of any of my medical notes may be looked at by responsible
	individuals from Imperial College London or from regulatory authorities where 
	it is relevant to my taking part in this research. I give permission for these individuals to 
	access my records that are relevant to this research.\hfill \framebox(20,12){}
  \item I consent to being contacted by the research team.\hfill \framebox(20,12){}
  \item I consent to my interview being recorded.  
      \hfill No \framebox(20,12){} Yes \framebox(20,12){}
  \item I consent to genetic testing as part of the research.\hfill \framebox(20,12){}
  \item I consent to storage of information and blood samples collected from me for future research.
      \hfill No \framebox(20,12){} Yes \framebox(20,12){}
  \item I consent to my GP and hospital care teams being informed of my participation in the research and, with my permission, of any clinically significant findings arising from the research.
      \begin{flushright} \framebox(20,12){} \end{flushright}
	
 \end{enumerate}

\vspace{0.1cm}

 \begin{tabular}{p{4cm}p{4cm}p{4cm}}
    \rule{10em}{.3pt} & \rule{10em}{.3pt} & \rule{10em}{.3pt} \\
     Name of subject  & Signature  & Date \\
 \end{tabular}

\vspace{0.1cm}

 \begin{tabular}{p{4cm}p{4cm}p{4cm}}
    \rule{10em}{.3pt} & &  \\
     Subject's date of birth  & &  \\
 \end{tabular}

\vspace{0.1cm}

 \begin{tabular}{p{4cm}p{4cm}p{4cm}}
    \rule{10em}{.3pt} & \rule{10em}{.3pt} & \rule{10em}{.3pt} \\
     Name of person taking consent (if different from Principle Investigator) & Signature &  Date \\
\end{tabular}

\vspace{0.1cm}

 \begin{tabular}{p{4cm}p{4cm}p{4cm}}
    \rule{10em}{.3pt} & \rule{10em}{.3pt} & \rule{10em}{.3pt} \\
     Principle Investigator & Signature &  Date \\
 \end{tabular}


\end{document}


